Supplementary Material for 'The complex network of trophic interactions in

### 2023-05-09 MS_ToSubmit/MS_Burdwood_foodweb.Rmd
Co-authors order

---
title: The complex network of trophic interactions in a subAntarctic oceanic Marine Protected
  Area
author:
  - name: Tomás I. Marina^a^
    email: tomasimarina@gmail.com
  - name: Irene R. Schloss^a^^,^^b^^,^^c^
  - name: Luciana Riccialdelli^a^
  - name: Fabiana L. Capitanio^f^
  - name: Sergio M. Delpiani^d^
  - name: Juan Martín Díaz de Astarloa^d^
  - name: Cintia Fraysse^a^
  - name: Gustavo A. Lovrich^a^
  - name: Andrea Raya Rey^a^^,^^c^^,^^e^
  - name: Mariela L. Spinelli^f^
  - name: Diego Urteaga^g^
  - name: Marcos Tatián^h^^,^^i^
  - name: Virginia A. García Alonso^f^
  - name: Claudia C. Boy^a^
  - name: Daniel O. Bruno^a^^,^^c^

>>>>

---
title: The complex network of trophic interactions in a subAntarctic oceanic Marine Protected
  Area
author:
  - name: Tomás I. Marina^a^
    email: tomasimarina@gmail.com
  - name: Irene R. Schloss^a^^,^^b^^,^^c^
  - name: Gustavo A. Lovrich^a^
  - name: Claudia C. Boy^a^
  - name: Daniel O. Bruno^a^^,^^c^
  - name: Fabiana L. Capitanio^f^
  - name: Sergio M. Delpiani^d^
  - name: Juan Martín Díaz de Astarloa^d^
  - name: Cintia Fraysse^a^
  - name: Virginia A. García Alonso^f^  
  - name: Andrea Raya Rey^a^^,^^c^^,^^e^
  - name: Mariela L. Spinelli^f^
  - name: Marcos Tatián^h^^,^^i^
  - name: Diego Urteaga^g^
  - name: Luciana Riccialdelli^a^

### 2023-05-09 MS_ToSubmit/SupMaterial.Rmd
Co-authors order

---
title: "Supplementary Material for 'The complex network of trophic interactions in
  a subAntarctic oceanic Marine Protected Area'"
author:
  - Tomás I. Marina
  - Irene R. Schloss
  - Luciana Riccialdelli
  - Fabiana L. Capitanio
  - Sergio M. Delpiani
  - Juan Martín Díaz de Astarloa
  - Cintia Fraysse
  - Gustavo A. Lovrich
  - Andrea Raya Rey
  - Mariela L. Spinelli
  - Diego Urteaga
  - Marcos Tatián
  - Virginia A. García Alonso
  - Claudia C. Boy
  - Daniel O. Bruno
bibliography: AMPBancoBurdwood.bib
output: pdf_document
---

>>>>

---
title: "Supplementary Material for 'The complex network of trophic interactions in
  a subAntarctic oceanic Marine Protected Area'"
author:
  - Tomás I. Marina
  - Irene R. Schloss
  - Gustavo A. Lovrich
  - Claudia C. Boy
  - Daniel O. Bruno  
  - Fabiana L. Capitanio
  - Sergio M. Delpiani
  - Juan Martín Díaz de Astarloa
  - Cintia Fraysse
  - Virginia A. García Alonso
  - Andrea Raya Rey
  - Mariela L. Spinelli
  - Marcos Tatián
  - Diego Urteaga
  - Luciana Riccialdelli
bibliography: AMPBancoBurdwood.bib
output: pdf_document
---
